Observations from Parallelising Three Maximum Common (Connected) Subgraph Algorithms

### 2017-07-31 paper/paper.tex
Convert from PASEO to IA3

\begin{abstract}
    We discuss our experiences adapting three recent algorithms for maximum common (connected) subgraph
    problems to exploit multi-core parallelism. We consider the effects of different work
    distribution strategies and their interaction with value-ordering heuristics, and propose a
    search method which is risk-free, reproducible, and scalable, as well as beneficial. Our results
    show that each algorithm can be parallelised successfully using this strategy, with the
    multi-core algorithms we create being clearly better than the sequential ones. We then look in
    more detail at the results, on an instance by instance basis, and discuss how we should be
    measuring speedups for these kinds of algorithm.
\end{abstract}

>>>>

\begin{abstract}
\end{abstract}
